\documentclass[11pt]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage{array}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{color}
\usepackage{xcolor}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.2}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% HEADER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\small \textbf{REFERRAL LETTER}}

\vspace{4pt}

{\fontsize{28}{30}\selectfont
\textcolor{blue!70!black}{\textbf{REFERRAL LETTER}}
}

\vspace{8pt}

\noindent
\fbox{
\parbox{\dimexpr\textwidth-2\fboxsep-2\fboxrule}{
\small
This fax may contain sensitive and confidential personal health information that is being sent for the sole use of the intended recipient. Unintended recipients are directed to securely destroy any materials received. You are hereby notified that the unauthorized disclosure or other unlawful use of this fax or any personal health information is prohibited. To the extent patient information contained in this fax is subject to 42 CFR Part 2, this regulation prohibits any unauthorized disclosure of these records. If you received this fax in error, please visit www.athenahealth.com/NotMyFax to notify the sender and confirm that the information will be destroyed. If you do not have internet access, please call 1-888-482-8436 to notify the sender and confirm that the information will be destroyed.
}
}

\vspace{10pt}

{\small [ID:A2B8F5E1]}

\vspace{10pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
{\LARGE \textbf{Lab Order}}

\vspace{3pt}

{\large April 29, 2026}
\end{center}

\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ORDER TO / PROVIDER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent
\begin{tabularx}{\textwidth}{|X|X|}
\hline
\textbf{Order To} &
\textbf{Ordering Provider}
\\
\hline

Thomas, Gutierrez and Long Laboratory Services &
Dr. Irwin, MD
\\

784 Martinez Estates Suite 717, Port Kristenhaven, LA 39638 &
82551 Erica Mountains, Fernandotown, VI 40784
\\

Phone: 488-396-5825
Fax: 109-762-2615
&
Phone: 440-011-7592
Fax: 330-734-7015
\\
\hline
\end{tabularx}

\vspace{-1pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ORDER SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tabularx}{\textwidth}{|X|}
\hline
\textbf{Order}
\\
\hline

Orders included:
Comprehensive Metabolic Panel (CMP)
$\bullet$
ICD-10:
T93
$\bullet$
Comprehensive Metabolic Panel (CMP)
$\bullet$
BILL:
Third Party

\\
\hline
\end{tabularx}

\vspace{-1pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PATIENT DETAILS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tabularx}{\textwidth}{|p{2.9in}|X|}
\hline
\textbf{Patient Name}
&
Cynthia Ford
\\
\hline

\textbf{Sex - DOB - Age}
&
F
\quad
05/11/1947
\quad
79
\\
\hline

\textbf{Address}
&
71418 Paul Oval, Bowersstad, MN 90583
\\
\hline

\textbf{Phone}
&
h: 016-713-1956
\quad
w: 376-690-1604
\\
\hline

\textbf{Primary Insurance}
&
Aetna - Policy: wWK93162774
\\
\hline

\textbf{Secondary Insurance}
&
None
\\
\hline

\textbf{Drawn by}
&
Karen Hicks
\\
\hline

\textbf{Date/Time Drawn}
&
04/29/2026 12:00 AM
\\
\hline

\textbf{Fasting?}
&
N/A
\\
\hline

\textbf{Other/Notes}
&
Patient has medication allergies - see chart
\\
\hline

\textbf{CC}
&
N/A
\\
\hline

\end{tabularx}

\vspace{35pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SIGNATURE BLOCK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}

Electronically Signed by:
Dr. Irwin, MD

\vspace{20pt}

\rule{4in}{0.5pt}

\vspace{12pt}

{\Large Dr. Irwin, MD}

\end{center}

\end{document}