\documentclass[11pt]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage{array}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{color}
\usepackage{xcolor}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.2}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% HEADER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\small \textbf{REFERRAL LETTER}}

\vspace{4pt}

{\fontsize{28}{30}\selectfont
\textcolor{blue!70!black}{\textbf{REFERRAL LETTER}}
}

\vspace{8pt}

\noindent
\fbox{
\parbox{\dimexpr\textwidth-2\fboxsep-2\fboxrule}{
\small
This fax may contain sensitive and confidential personal health information that is being sent for the sole use of the intended recipient. Unintended recipients are directed to securely destroy any materials received. You are hereby notified that the unauthorized disclosure or other unlawful use of this fax or any personal health information is prohibited. To the extent patient information contained in this fax is subject to 42 CFR Part 2, this regulation prohibits any unauthorized disclosure of these records. If you received this fax in error, please visit www.athenahealth.com/NotMyFax to notify the sender and confirm that the information will be destroyed. If you do not have internet access, please call 1-888-482-8436 to notify the sender and confirm that the information will be destroyed.
}
}

\vspace{10pt}

{\small [ID:4DB86EED]}

\vspace{10pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
{\LARGE \textbf{Lab Order}}

\vspace{3pt}

{\large May 20, 2026}
\end{center}

\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ORDER TO / PROVIDER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent
\begin{tabularx}{\textwidth}{|X|X|}
\hline
\textbf{Order To} &
\textbf{Ordering Provider}
\\
\hline

Brown, Miller and Anderson Laboratory Services &
Dr. Gamble, MD
\\

719 Rachel Divide, West Jeremy, ND 16579 &
467 Hill Street, Ashleyburgh, IA 21897
\\

Phone: 204-148-7610
Fax: 638-759-9316
&
Phone: 698-516-9970
Fax: 749-612-7949
\\
\hline
\end{tabularx}

\vspace{-1pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ORDER SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tabularx}{\textwidth}{|X|}
\hline
\textbf{Order}
\\
\hline

Orders included:
Complete Blood Count (CBC) with Differential
$\bullet$
ICD-10:
Z58.74
$\bullet$
Complete Blood Count (CBC) with Differential
$\bullet$
BILL:
Medicare

\\
\hline
\end{tabularx}

\vspace{-1pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PATIENT DETAILS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tabularx}{\textwidth}{|p{2.9in}|X|}
\hline
\textbf{Patient Name}
&
Walter Schaefer
\\
\hline

\textbf{Sex - DOB - Age}
&
M
\quad
06/30/1949
\quad
76
\\
\hline

\textbf{Address}
&
24118 Rice Cliffs Suite 331, Lynnhaven, FM 36426
\\
\hline

\textbf{Phone}
&
h: 361-630-7501
\quad
w: 720-668-6340
\\
\hline

\textbf{Primary Insurance}
&
Cigna - Policy: tob66669664
\\
\hline

\textbf{Secondary Insurance}
&
None
\\
\hline

\textbf{Drawn by}
&
Lindsay Austin
\\
\hline

\textbf{Date/Time Drawn}
&
05/21/2026 12:00 AM
\\
\hline

\textbf{Fasting?}
&
No
\\
\hline

\textbf{Other/Notes}
&
Patient has medication allergies - see chart
\\
\hline

\textbf{CC}
&
N/A
\\
\hline

\end{tabularx}

\vspace{35pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SIGNATURE BLOCK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}

Electronically Signed by:
Dr. Gamble, MD

\vspace{20pt}

\rule{4in}{0.5pt}

\vspace{12pt}

{\Large Dr. Gamble, MD}

\end{center}

\end{document}